\documentclass[a4paper]{article}
\usepackage{amssymb,textcomp,fullpage,resume}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}

\begin{document}
    %==== Contact Info ====%
    \contact{Emeka Nkurumeh}{Pasadena, CA}{e.nk@caltech.edu}{(405) 546-6190}{@emekoi}

    %==== Education ====%
    \header{Education}
    \begin{school}{California Institute of Technology}{Pasadena, CA}{3.3}{Sep 2021 - June 2025}
        \item Programming Fundamentals, Methods, and Software Design (CS 1-4), Decidability and Tractability (CS 21), Algorithms (CS 38), Interactive Theorem Proving (CS 128), Programming Languages (CS 131), Compilers (CS 164)
        \item Calculus and Linear Algebra (Ma 1), Differential Equations (Ma 2), Abstract Algebra (Ma 5), Discrete Math (Ma 6), Graduate Probability (Ma 140)
    \end{school}
    \header{Awards}
    \begin{award*}{Gates Scholar}{Apr 2021}{The Bill \& Melinda Gates Foundation}
    \end{award*}
    \begin{award*}{QuestBridge National College Match Scholar}{Dec 2020}{QuestBridge}
    \end{award*}

    \header{Skills}
    \begin{skill}{Programming Languages}
      \begin{itemize}[nosep]
        \item Haskell, OCaml, Coq, C, Zig, Java, Nim, Python, Rust, x86/x86\_64 Assembly, Lua, \LaTeX
      \end{itemize}
    \end{skill}
    \begin{skill}{Unix Operating Systems}
      \begin{itemize}[nosep]
        \item Bash, Fish, Vim, Emacs, Git, gdb, Linux, various Unix command line programs
     \end{itemize}
    \end{skill}

    \header{Research Experience}
    \begin{activity}{Simulation of Site Percolation on 2D Lattices}{Oklahoma City, Oklahoma}{Programmer}{Aug 2020 - Dec 2020}{OSSM}
      \begin{itemize}[topsep=5pt, partopsep=0pt, itemsep=-1pt]
        \item Created and optimized a visualizer fo site percolation on 2D lattices for use in calculating critical thresholds for spanning clusters.
        \item Started work on an interactive visualizer for site percolation in higher dimensional lattices.
      \end{itemize}
    \end{activity}

    \begin{activity}{University of Pennsylvania REPL}{}{Programmer}{Aug 2020 - Dec 2020}{OSSM}
      \begin{itemize}[topsep=5pt, partopsep=0pt, itemsep=-1pt]
        \item Created and optimized a visualizer fo site percolation on 2D lattices for use in calculating critical thresholds for spanning clusters.
        \item Started work on an interactive visualizer for site percolation in higher dimensional lattices.
      \end{itemize}
    \end{activity}

    \header{Projects and Extracurriculars}
    \begin{activity}{Zig Programming Language Development}{Oklahoma City, OK}{Open Source Contributor}{Sept 2018 - Sept 2023}{Zig Programming Language Project}
      \begin{itemize}[topsep=5pt, partopsep=0pt, itemsep=-1pt]
        \item Contributed to standard library, various stages of the bootstrapping compiler, and improved support for non-MSVC based build environments on Windows.
        \item Reported several bugs and made multiple influential language proposals.
      \end{itemize}
    \end{activity}

    \begin{activity}{Brainf*ck Compiler}{}{}{Dec 2021}{}
      \begin{itemize}[topsep=5pt, partopsep=0pt, itemsep=-1pt]
        \item Implemented a dependency-free Brainf*ck interpreter and compiler with support for outputting ELF executables with no dependency on any system libraries.
        \item Implemented several optimizations leading to a 2-5x performance increase over the baseline compiler and a reduction of the number of syscalls needed for IO-bound programs.
      \end{itemize}
    \end{activity}

    \begin{activity}{Unlambda Interpreter}{}{}{Mar 2022}{}
      \begin{itemize}[topsep=5pt, partopsep=0pt, itemsep=-1pt]
        \item Wrote an Unlambda interpreter using a modified CEK machine to capture and restore continuations.
        \item Started work on a graph rewriting based approach for interpretation of Unlambda code and compilation to imperative languages such as x86\_64 assembly.
      \end{itemize}
    \end{activity}

    % \begin{activity}{Bidirectional Type Checkers}{}{}{Jul 2022 - Mar 2023}{}
    %   Implemented type checkers for the bidirectional type systems presented in
    %   \begin{itemize}[topsep=5pt, partopsep=0pt, itemsep=-1pt]
    %     \item \textit{A Mechanical Formalization of Higher-Ranked Polymorphic Type Inference}
    %     \item \textit{Complete and Easy Bidirectional Typechecking for Higher-Rank Polymorphism}
    %     \item \textit{Let Arguments Go First}
    %   \end{itemize}
    % \end{activity}
\end{document}
